Rust for Scientific Computing

### 2025-08-22 main.tex
add new images
add new crates; distribute remaining points onto sections

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/stackoverflow-popular-languages.pdf}%
    \includegraphics[width=0.5\textwidth]{figures/pypi-org-used-languages.pdf}
    \caption{TODO}
\end{figure}

@@

\begin{enumerate}
    \item Linear Algebra \& Arrays (nalgebra, ndarray, ...)
    \item Statistics \& Data Analysis (statrs, ndarray-stats, smartcore, ...)
    \item Symbolic \& other Math (num, rug, speciyl, symcc)
    \item ODE solvers~\cite{Renevey2024}, Diffsol
    \item PDE solvers
    \item Fluid Dynamics: Salva (2D \& 3D)~\cite{Crozet2024}
    \item Physics Engine: Rapier (2D \& 3D)~\cite{Crozet2025}
    \item Meshing (honeycomb)
    \item Plotting (plotters, plotlib, gnuplot bindings, vtk-rs)
    \item Utilities (rayon, lapack)
    \item GPU (rust-cuda, wgpu)
    \item Datastructures
    \item Optimization
\end{enumerate}

@@

\subsubsection{Statistics \& Probability}
(statsrs, ndarray-stats, smartcore)

@@

@@

@@

\subsection{Visualization}
\subsubsection{Plotting (2D)}
\subsubsection{3D Rendering}
\subsubsection{Interactive}
(dioxus)

@@

RLST\\
Linear algebra frameworks in Rust for the solution of partial differential equations.

@@

Bernstein–Bézier\\
Finite elements for RMM in Rust. ResearchGate

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/stackoverflow-popular-languages.pdf}%
    \includegraphics[width=0.5\textwidth]{figures/pypi-org-used-languages.pdf}
    \includegraphics[width=0.5\textwidth]{figures/stackoverflow-loved-language.pdf}%
    \includegraphics[width=0.5\textwidth]{figures/stackoverflow-desired-language.pdf}
    \caption{TODO}
\end{figure}

@@

@@

\subsubsection{Statistics \& Probability}
(statrs, ndarray-stats, smartcore)

@@

ODE solvers~\cite{Renevey2024}, Diffsol

@@

salva (2D \& 3D)~\cite{Crozet2024}

Rapier (2D \& 3D)~\cite{Crozet2025}

@@

\subsection{Visualization}
\subsubsection{Plotting (2D)}
plotters, plotlib, gnuplot bindings

\subsubsection{3D Rendering}
vtk-rs

Meshing (honeycomb)

\subsubsection{Interactive}
(dioxus)

@@

rlst\\
The Rust Linear Solver toolbox is an in-development project for dense and sparse linear algebra routines in Rust.

@@

Bernstein–Bézier\\
Finite elements for RMM in Rust~\cite{Sky2024}

mwa\_hyperdrive\\
Calibration software for the Murchison Widefield Array (MWA) radio telescope.
\url{https://mwatelescope.github.io/mwa_hyperdrive/index.html}

alg\_tools\\
utility routines and tools for implementing iterative algorithms and (abstract) numerical computing in Rust~\cite{Valkonen2023}.
\url{https://tuomov.iki.fi/software/alg_tools/}

clarabel\\
Clarabel is an interior point numerical solver for convex optimization problems using a novel
homogeneous embedding~\cite{Clarabel_2024}.

fips\\
\cite{jeggle2023genericframeworkdataracefreemanyparticle}
\url{https://zenodo.org/records/6757615}
